\documentclass[10pt,a4paper,ragged2e,withhyper]{altacv}

\geometry{left=1.25cm,right=1.25cm,top=1.5cm,bottom=1.5cm,columnsep=1cm}

\usepackage{paracol}
\usepackage[a-1b]{pdfx}
\usepackage{simpleicons}
\usepackage{csquotes}
\usepackage[dvipsnames]{xcolor}

\begin{filecontents*}{\jobname.xmpdata}
    \Title{CV - Tomáš Režňák}
    \Author{Tomáš Režňák}
    \Subject{Curriculum Vitae}
\end{filecontents*}

\iftutex
  \setmainfont{Roboto Slab}
  \setsansfont{Lato}
  \renewcommand{\familydefault}{\sfdefault}
\else
  \usepackage[rm]{roboto}
  \usepackage[defaultsans]{lato}
  \renewcommand{\familydefault}{\sfdefault}
\fi

\colorlet{name}{black}
\colorlet{tagline}{NavyBlue}
\colorlet{heading}{black}
\colorlet{headingrule}{NavyBlue}
\colorlet{subheading}{black}
\colorlet{accent}{black}
\colorlet{emphasis}{black}
\colorlet{body}{darkgray}

\renewcommand{\namefont}{\Huge\rmfamily\bfseries}
\renewcommand{\personalinfofont}{\footnotesize}
\renewcommand{\cvsectionfont}{\LARGE\rmfamily\bfseries}
\renewcommand{\cvsubsectionfont}{\large\bfseries}
\renewcommand{\cvItemMarker}{\small\textbullet}
\renewcommand{\cvRatingMarker}{\faCircle}

\begin{document}
\name{Tomáš Režňák}
\tagline{Software Developer}

\personalinfo{%
	\location{Velké Meziříčí, Czech Republic}
	\email{tomas.reznak@proton.me}
	\linkedin{reznakt}
	\github{reznakt}
	\printinfo{\faGitlab}{reznakt}[https://gitlab.com/reznakt]
}

\makecvheader
\bigskip
\columnratio{0.5}

\begin{paracol}{2}
	\cvsection{Experience}

	\cvevent{\href{https://siemens.com/}{Siemens}}{Associate Software Engineer}{May 2022 -- Sep 2024}{Brno}
	\begin{itemize}
		\item Worked as a backend developer in a team of 6 to create a web application for remote control of industrial power supply units (PSUs) and uninterruptible power supplies (UPSs).
		\item Used industrial communication protocols such as \href{https://profinetuniversity.com/naming-addressing/profinet-dcp/}{DCP} and \href{https://opcfoundation.org/about/opc-technologies/opc-ua/}{OPC UA} to communicate with devices.
		\item Used \href{https://www.typescriptlang.org/}{TypeScript}, \href{https://nodejs.org/}{Node.js}, and \href{https://expressjs.com/}{Express} to create RESTful APIs for the application.
		\item Used \href{https://gitlab.com/}{GitLab} to set up a complex CI/CD pipeline for the project.
		\item Regularly participated in code reviews and provided feedback to team members.
		\item Used tools such as \href{https://turborepo.com/}{TurboRepo} and \href{https://pnpm.io/}{pnpm} to manage project builds and dependencies.
		\item Interviewed candidates for the team and provided feedback on their technical skills.
	\end{itemize}

	\divider

	\cvevent{\href{https://cdv.cz/}{Centrum dopravního výzkumu, v. v. i.}}{Data entry}{Jul 2019 --- Aug 2019}{Brno}
	\begin{itemize}
		\item Analyzed traffic data and entered it into a database.
		\item Worked on a project to analyze traffic data in selected areas of the Czech Republic and Slovakia.
		\item Worked on a project to analyze traffic signs to aid in the development of autonomous vehicles.
	\end{itemize}

	\bigskip
	\cvsection{Education}

	\cvevent{Master's degree \textbullet\ Machine learning and artificial intelligence}{\href{https://fi.muni.cz/}{Faculty of Informatics, Masaryk University}}{Sep 2025 -- \textbf{present}}{Brno}

	\divider

	\cvevent{Bachelor's degree \textbullet\ Programming and development}{\href{https://fi.muni.cz/}{Faculty of Informatics, Masaryk University}}{Sep 2021 -- Jun 2025}{Brno}
	\faMedal Dean's Award for an Outstanding Final Thesis \\ \quad (\href{https://is.muni.cz/th/ddfps/}{\enquote{A Manipulation Library for Scalable Vector Graphics}})

	\switchcolumn

	\cvsection{Strengths \& interests}
	\smallskip

	\cvtag{\faEye Eye for detail}
	\cvtag{\faBolt Enthusiastic}
	\cvtag{\faAdjust Versatile}
	\cvtag{\faBook Quick learner}
	\cvtag{\faUser Self-reliant}
	\cvtag{\faLightbulb Innovative}
	\cvtag{\faClipboardCheck Good sense for code quality}

	\divider

	\cvtag{\faCode Programming}
	\cvtag{\faLinux Linux}
	\cvtag{\faGithub Open-source}
	\cvtag{\faServer Self-hosting}
	\cvtag{\faFilm TV shows}
	\cvtag{\faGamepad Gaming} \\
	\cvtag{\faMusic Music}
	\cvtag{\faSwimmer Swimming}

	\medskip

	\cvsection{Technology}
	\smallskip

	\href{https://python.org/}{\cvtag{\faPython Python}}
	\cvtag{\faJs JavaScript}
	\href{https://typescriptlang.org/}{\cvtag{\faJs TypeScript}}
	\cvtag{\simpleicon{c} C}
	\href{https://nodejs.org/}{\cvtag{\faNodeJs Node}}
	\href{https://docker.com/}{\cvtag{\faDocker Docker}}
	\href{https://github.com/}{\cvtag{\faGithub GitHub}}
	\href{https://gitlab.com/}{\cvtag{\faGitlab GitLab}}
	\href{https://git-scm.com/}{\cvtag{\faGit* Git}}
	\cvtag{\simpleicon{gnubash} Bash}
	\href{https://kernel.org/}{\cvtag{\faLinux Linux}}
	\href{https://bun.sh/}{\cvtag{\simpleicon{bun} Bun}}
	\href{https://nestjs.com/}{\cvtag{\simpleicon{nestjs} Nest}}
	\href{https://react.dev/}{\cvtag{\faReact React}}
	\href{https://expressjs.com/}{\cvtag{\simpleicon{express} Express}}
	\href{https://prisma.io/}{\cvtag{\simpleicon{prisma} Prisma}}
	\href{https://latex-project.org/}{\cvtag{\simpleicon{latex} \LaTeX}}

	\medskip
	\cvsection{Languages}
	\smallskip

	\cvskill{Czech}{5}
	\medskip
	\cvskill{English}{4.5}

	\medskip
	\cvsection{Projects}

	\cvevent{\href{https://github.com/reznakt/svglab}{\faGithub svglab}}{}{}{}
	\begin{itemize}
		\item A Python library for manipulating and optimizing SVG documents.
		\item Created as a part of my bachelor's thesis.
		\item Supports all SVG elements and attributes, unlike other libraries that only support a subset of SVG.
		\item Has the potential to become the new standard for SVG manipulation in the Python ecosystem.
	\end{itemize}

	\divider

	\cvevent{\href{https://github.com/reznakt/dotfiles}{\faGithub dotfiles}}{}{}{}
	\begin{itemize}
		\item A collection of my personal configuration files for my Linux machines.
		\item Includes configuration files for \href{https://neovim.io/}{Neovim}, \href{https://www.zsh.org/}{Zsh}, \href{https://hyprland.org/}{Hyprland}, \href{https://nixos.org/}{NixOS}, and many more.
		\item Allows me to declaratively manage my system configuration and easily replicate it on all my machines.
	\end{itemize}

	\divider

	\cvevent{\href{https://github.com/reznakt/ray-casting}{\faGithub ray-casting}}{}{}{}
	\begin{itemize}
		\item A simple \href{https://en.wikipedia.org/wiki/Ray_casting}{ray-caster} built with C99 and \href{https://www.libsdl.org/}{SDL2}.
		\item Includes a test runner made from scratch.
		\item Built with \href{https://emscripten.org/}{Emscripten} to allow people to play online.
	\end{itemize}
\end{paracol}
\end{document}
